---
title: "An Introduction to Writing Reproducible Manuscripts Using RMarkdown"
author: "Hao Ye"
institute: "Health Science Center Libraries, University of Florida"
date: "(updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#09274B",
  base_font_size = "32px", 
  header_h1_font_size = "2.0rem",
  header_h2_font_size = "1.5rem",
  header_h3_font_size = "1.25rem", 
  header_background_content_padding_top = "2rem", 
  header_font_google = google_font("Lato"),
  text_font_google   = google_font("Montserrat", "300", "300i", "500"),
  code_font_google   = google_font("Source Code Pro", "300", "500"), 
  extra_css = list("p" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "ul" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "li" = list("margin-block-start" = "0.5em", 
                              "margin-block-end" = "0.5em"), 
                   "pre" = list("margin-top" = "0.5em", 
                              "margin-bottom" = "0.5em")), 
  link_color = "#339944"
)
```
class: inverse, center, middle

# `r rmarkdown::metadata$title`
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$institute`
### (updated: `r Sys.Date()`)

---

# Learning Objectives

* describe the principles of reproducible documents
* apply the syntax of markdown to format text
* format numerical results in R Markdown
* format tables in R Markdown
* generate figures in R Markdown
* format references in R Markdown

---
class: inverse, center, middle

# Reproducible Documents

---

# Overview

Reproducible Documents:

* a tool to embed text with other outluts
  - code, figures, tables
* authors only make changes in *one* place
  - the entire document stays up to date
  - (instead of redoing an analysis, and copying images and numbers into MS Word)

---

# Many Platforms Exist:

* [Manubot](https://github.com/manubot/rootstock)
* [Stencila](https://stenci.la/)
* [Jupyter Notebooks](https://jupyter.org/)

--

We are going to talk about [R Markdown](https://rmarkdown.rstudio.com/) !
* many add-ons extend functionality
* *This lesson* is only a basic intro

---
class: inverse, center, middle

# How R Markdown Works

---





---
class: inverse, center, middle

# Syntax

---
class: inverse, center, middle

# Extensions

---

# Thanks

* Let me know what content you'd like to see
* Contact me for additional questions or consultation requests!
* Check back in on the libguide for more modules and contact info:
  - https://guides.uflib.ufl.edu/reproducibility

